hbm_paper_results

### 2024-02-08 paper_prop_results.Rmd
checking over, adding featurewise sex-bias tests

```{r}
cent.subj.mean.test.df <- fread(paste0(der_path, "/ukb_ratio/subj.abs.mean_sex_bias_cent_t_tests.csv"))
cent.subj.mean.test.df <- cent.subj.mean.test.df %>%
  mutate(prop = factor(prop, levels=c("0M:10F", "1M:9F", "2M:8F", "3M:7F", "4M:6F", "5M:5F", "6M:4F", "7M:3F", "8M:2F", "9M:1F", "10M:0F"), ordered=TRUE),
         dataset = as.factor(dataset))
cent.subj.mean.test.df
```

@@

@@

full_join(noext.cent.t.test.df_reduced, cent.t.test.df_reduced) %>%
  ggplot() +
  geom_col(aes(x=prop, y=n_sig_regions, fill=as.factor(full_df)), position="dodge") +
  facet_wrap(~comp) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```
Test sex-biases in centile errors w/in each feature
**COME BACK TO THIS**

@@

Test w/in feature sex-biases in errors (diff_list) using `featurewise_sex_bias_test.R`, saved as `full_featurewise_cent_sex_bias_tests.RDS`
**RERUNNING TO KEEP PROP VALS AS EXPLICIT NAMES, COME BACK TO THIS**

@@

full_join(noext.z.t.test.df_reduced, z.t.test.df_reduced) %>%
  ggplot() +
  geom_col(aes(x=prop, y=n_sig_regions, fill=as.factor(full_df)), position="dodge") +
  facet_wrap(~comp) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```
Test sex-biases in z errors w/in each feature
**COME BACK TO THIS**

## FIGURE 4
```{r}
fig_4 <- ggarrange(ggarrange(sampling.plt, prop.global_cent_errs_plot, 
                             nrow = 2, labels = c("A", "B"),
                             heights=c(1,2)), #nest 1st col
          sex_err_ratio.plt,
          ncol = 2,
          widths=c(1.1, 1),
          labels = c(NA, "C")                                    
)

>>>>

```{r}
cent.subj.mean.test.df <- fread(paste0(der_path, "/ukb_ratio/subj.abs.mean_sex_bias_cent_t_tests.csv"))
cent.subj.mean.test.df <- cent.subj.mean.test.df %>%
  mutate(prop = factor(prop, levels=c("0M:10F", "1M:9F", "2M:8F", "3M:7F", "4M:6F", "5M:5F", "6M:4F", "7M:3F", "8M:2F", "9M:1F", "10M:0F"), ordered=TRUE),
         dataset = as.factor(dataset))
# cent.subj.mean.test.df
```

@@

look at just cf.gam & cf.gamlss

```{r, eval=FALSE}
cent.subj.sex.test.df %>%
  dplyr::filter(dataset == "cf.gamlss") %>%
  dplyr::select(pheno, prop, sig_fdr) %>%
  arrange(pheno, prop)
```

@@

full_join(noext.cent.t.test.df_reduced, cent.t.test.df_reduced) %>%
  ggplot() +
  geom_col(aes(x=prop, y=n_sig_regions, fill=as.factor(full_df)), position="dodge") +
  facet_wrap(~comp) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```
Test sex-biases in centile errors w/in each feature
```{r}
noext_cent.subj.sex.test.list <- readRDS(paste0(der_path, "/ukb_ratio/no.ext_featurewise_cent_sex_bias_tests.RDS"))
noext_cent.subj.sex.test.df <- bind_rows(noext_cent.subj.sex.test.list)
```

```{r}
noext_cent.subj.sex.test.df %>%
  ggplot() +
  geom_bar(aes(x=prop, fill=sig_fdr)) +
  facet_wrap(~dataset) +
  scale_x_discrete(labels=percent_f) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

@@

```{r}
z.subj.sex.test.list <- readRDS(paste0(der_path, "/ukb_ratio/full_featurewise_z_sex_bias_tests.RDS"))
z.subj.sex.test.df <- bind_rows(z.subj.sex.test.list)
```

```{r}
z.subj.sex.test.df %>%
  ggplot() +
  geom_bar(aes(x=prop, fill=sig_fdr)) +
  facet_wrap(~dataset) +
  scale_x_discrete(labels=percent_f) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

@@

full_join(noext.z.t.test.df_reduced, z.t.test.df_reduced) %>%
  ggplot() +
  geom_col(aes(x=prop, y=n_sig_regions, fill=as.factor(full_df)), position="dodge") +
  facet_wrap(~comp) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```
Test sex-biases in z errors w/in each feature

```{r}
noext_z.subj.sex.test.list <- readRDS(paste0(der_path, "/ukb_ratio/no.ext_featurewise_z_sex_bias_tests.RDS"))
noext_z.subj.sex.test.df <- bind_rows(noext_z.subj.sex.test.list)
```

```{r}
noext_z.subj.sex.test.df %>%
  ggplot() +
  geom_bar(aes(x=prop, fill=sig_fdr)) +
  facet_wrap(~dataset) +
  scale_x_discrete(labels=percent_f) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

## FIGURE 4
```{r}
fig_4 <- ggarrange(ggarrange(sampling.plt, prop.global_cent_errs_plot, 
                             nrow = 2, labels = c("A", "C"),
                             heights=c(1,2)), #nest 1st col
          sex_err_ratio.plt,
          ncol = 2,
          widths=c(1.1, 1),
          labels = c(NA, "B")                                    
)
